\section{Hubble's Law and SN Ia Cosmology}

\subsection{What the heck is a rest frame?}

Let's say you have some data, but it's from a supernova with $z = 0.1$. Because of the relativistic Doppler effect, the wavelengths you \textit{observe} are different from the ``actual'' wavelengths, i.e., rest frame wavelengths. This will also affect observed flux. Ignoring ejecta velocity (see \textcolor{red}{CHAPTER FOR THIS}), this is why a spectral line won't appear in its ``expected'', or rest frame, position. Usually, you want to put your spectra in the rest frame before doing anything with them because it's hard to compare SNe at different redshifts. See Section~\ref{sec:spec_restframe} for details on correcting SN spectra to the rest frame. 

\subsection{$z_{helio}$ and $z_{CMB}$}

You'll encounter two kinds of redshift---heliocentric redshift ($z_{helio}$) and CMB (Cosmic Microwave Background) redshift ($z_{CMB}$). \textit{These are different, and are used for different purposes!} $z_{CMB}$ is the redshift caused by the Universe's expansion \textit{only}, i.e., where the reference frame is the CMB frame. $z_{helio}$ is the redshift with \textit{only} the Earth's rotation and orbit removed. There are still effects from other motion, like Galactic rotation and the Galaxy moving around with respect to other objects, as well as $z_{CMB}$. ``Heliocentric'' $\equiv$ ``Sun at center'', so ``Sun at center'' is the rest frame. It's how things are moving relative to the Milky Way. Note that $z_{helio}$, while often reported as an object's redshift, is \textit{not} the observed redshfit. The observed redshift does not have the Earth's rotation and orbit removed. In other words, $z_{helio}$ contains information about a bunch of things moving relative to each other, including motion relative to the CMB, while $z_{CMB}$ contains information about \textit{only} motion relative to the CMB.

For cosmology, you'll use $z_{CMB}$ (e.e., when making a Hubble diagram or determining other cosmological parameters). If you're dealing with data that you need to correct to the rest frame, you probably want to use $z_{helio}$.